\chapter*{\Huge\textbf{ABSTRACT}}

\hspace{3em} In the Modern Era of fast moving technology we can do things which we never thought we could do before. But to achieve and accomplish these thoughts there is a need for a platform which can automate all our tasks with ease and comfort.\\

\noindent
Thus we need to develop a Personal AI having brilliant powers of deduction and the ability to interact with our surroundings just by one of the materialistic form of human interaction, our VOICE. The Hardware device captures the personals audio request through microphone and  processes the request so that the device can respond to the individual using in-built speaker module. For Example, if you ask the device 'what's the weather?' or 'how's traffic?' using its built-in skills, it looks up the weather and traffic status respectively and then returns the response to the customer through connected speaker.\\

\noindent
The platform is open to all and it can connect all IOT devices in the vicinity. This feature makes it distinctive from already existing personal AI’s and separates it from the flock. It uses open source software to process natural language, to determine the intent of the query and to perform the action. The platform features include : Turn on the lights, do the mathematics, play your favorite song, check the weather, connect IoT devices, basically answer to all your logical questions. Just speak naturally and the platform is there to do your bidding.\\

\noindent
The Platform also extends an Android Application in which you can add a To-Do-list or set a reminder or alarm through the app, push notifications and personalize according to your needs. The device has a lot of native skills and abilities baked in it and more can be added to extend its capabilities.\\

\noindent
There is still a lot of ground to be covered up in the world of automation but the skills of our device can help to build a new generation of voice controlled devices and bring a new sustaining change in the field of automation.\\
